Modelling last glacial cycle ice dynamics in the Alps

### 2017-09-19 articles/cycle/alps-cycle.tex
Wrap lists of figs and tables in temporary notes.

    Table~\ref{tab:params} -- Model parameters.\\
    Fig.~\ref{fig:inputs} -- Climate and geothermal model inputs.\\

@@

    Table~\ref{tab:records} -- Palaeo-climate records.\\
    Fig.~\ref{fig:timeseries} -- Low-resolution time series.\\
    Fig.~\ref{fig:footprints} -- Low-resolution ice cover.\\

@@

    Fig.~\ref{fig:lgmvel} -- Snapshot at 21\,ka and volume time series.\\
    Fig.~\ref{fig:timing} -- Timing of the LGM and area time series.\\
    Fig.~\ref{fig:trimlines} -- LGM ice thickness compared to trimlines.\\
    Fig.~\ref{fig:profiles} -- Individual glacier extent profiles.

>>>>

    \note{This section contains\\
        Table~\ref{tab:params} -- Model parameters.\\
        Fig.~\ref{fig:inputs} -- Climate and geothermal model inputs.}

@@

    \note{This section contains\\
      Table~\ref{tab:records} -- Palaeo-climate records.\\
      Fig.~\ref{fig:timeseries} -- Low-resolution time series.\\
      Fig.~\ref{fig:footprints} -- Low-resolution ice cover.}

@@

    \note{This section contains\\
        Fig.~\ref{fig:lgmvel} -- Snapshot at 21\,ka and volume time series.\\
        Fig.~\ref{fig:timing} -- Timing of the LGM and area time series.\\
        Fig.~\ref{fig:trimlines} -- LGM ice thickness compared to trimlines.\\
        Fig.~\ref{fig:profiles} -- Individual glacier extent profiles.}
